SubsidyExplorer - Step 6: Run Model

### 2020-09-05 scripts/07_proposals.Rmd
individual proposal results

```{r}
proposal_results <- NULL
i <- 2
for(i in 2:length(proposal_choices)){

@@

@@

   ### Find fleets
    fleet <-  CreateFleets(
      vessel_list = vessel_dat,
      iuu = iuu,
      oa = oa,
      overcap = overcap,
      cap_tier = cap_tier,
      managed_threshold = managed_cutoff,
      subsidy_types_all = subsidy_types_sorted_sumaila,
      cap_tier_lookup = cap_tier_lookup,
      country_lookup = country_dependencies)

@@

    # Extract results timeseries
    results_all <- results %>%
      dplyr::filter(Year > 2018) %>%
      group_by(Year, Variable, Fleet) %>%
      mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU) / abs(BAU),
      TRUE ~ 0)) %>%
      ungroup() %>%
      mutate(run_id = proposal_name,
             run_name = names(proposal_name))

@@

>>>>

```{r}
proposal_results <- NULL

for(i in 2:length(proposal_choices)){

@@

  print(proposal_name)

@@

   ### Find fleets
    fleet <-  CreateFleets(
      vessel_list = vessel_dat,
      iuu = iuu,
      oa = oa,
      overcap = overcap,
      cap_tier = cap_tier,
      managed_threshold = managed_cutoff,
      subsidy_types_all = subsidy_types_sorted_sumaila,
      cap_tier_lookup = cap_tier_lookup_table,
      country_lookup = country_dependencies)

@@

    # Extract results timeseries
    results_all <- results %>%
      dplyr::filter(Year > 2018) %>%
      group_by(Year, Variable, Fleet) %>%
      mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU) / abs(BAU),
      TRUE ~ 0)) %>%
      ungroup() %>%
      mutate(run_id = proposal_name,
             run_name = names(proposal_name),
             run_group = unique(proposal_settings$category[proposal_settings$proposal == proposal_name]))

@@

```{r}
most_ambitious_results <- read_csv(paste0(here::here("results", "06-run-model/"), "rel_subs_all_B_ts.csv")) %>%
  mutate(run_group = "Ambitious Reform")

most_ambitious_results_global <- most_ambitious_results %>%
  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
    summarize(BAU_tot = sum(BAU, na.rm = T),
              Reform_tot = sum(Reform, na.rm = T),
              Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
                            TRUE ~ 0)) %>%
    ungroup() %>%
    mutate(Region = "Global") %>%
    mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue")) %>%
  dplyr::filter(Fleet == "Total") %>%
  dplyr::filter(Variable %in% c("Biomass", "Catches", "Revenue"))

plot_results <- proposal_results %>%
  dplyr::filter(run_id != "RD/TN/RL/103") %>%
  bind_rows(most_ambitious_results)

# Make plots
if(make_plots){

  # 1) global (aggregated) timeseries plot
  compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
                                           spatial_res = "global",
                                           temporal_res = "all",
                                           start_year = 2018,
                                           end_year = 2100,
                                           plot_name = "all_proposals_ts_plot",
                                           plot_width = 8,
                                           plot_height = 6.5,
                                           results_dir = results_dir,
                                           compare = TRUE)

  # 2) global (aggregated) "kobe" final year plot
  compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
                                            spatial_res = "global",
                                            temporal_res = "last",
                                            end_year = 2100,
                                            plot_name = "all_proposals_end_plot",
                                            plot_width = 8,
                                            plot_height = 6.5,
                                            results_dir = results_dir,
                                            compare = TRUE)

  # 3) regional timeseries plot
  regional_compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
                                                    spatial_res = "regional",
                                                    temporal_res = "all",
                                                    start_year = 2018,
                                                    end_year = 2100,
                                                    plot_name = "regional_all_proposals_ts_plot",
                                                    plot_width = 8,
                                                    plot_height = 6.5,
                                                    results_dir = results_dir,
                                                    compare = TRUE)

  # 4) regional "kobe" final year plot
  regional_compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
                                                     spatial_res = "regional",
                                                     temporal_res = "last",
                                                     end_year = 2100,
                                                     plot_name = "regional_all_proposals_end_plot",
                                                     plot_width = 8,
                                                     plot_height = 6.5,
                                                     results_dir = results_dir,
                                                     compare = TRUE)
}
```
